DRAFT: Scalable, Robust Multipath Communication on the Butterfly Network

### 2018-05-18 plosone/attack.tex
Add plosone draft.

\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{epigraph}
\usepackage[utf8]{inputenc}
\usepackage{afterpage}
\usepackage{tikz}
\usepackage{soul}
\usepackage[framemethod=tikz]{mdframed}
\usetikzlibrary{arrows,chains,decorations.pathreplacing}
\usepackage{pifont}% http://ctan.org/pkg/pifont

\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}
\newcommand{\bhlpar}{\begin{mdframed}[innerleftmargin=0,innerrightmargin=0,hidealllines=true,backgroundcolor=yellow!20]}
\newcommand{\ehlpar}{\end{mdframed}}
\DeclareMathOperator{\wbf}{wBF}
\newtheorem{theorem}{Theorem}

\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[WEBCONF'18]{The Web Conference}{April 2018}{Lyon, France} 
\acmYear{2018}
\copyrightyear{2018}

\acmArticle{4}
\acmPrice{15.00}

\begin{document}
\title{
    Towards Attack-Tolerant Networks:
    Concurrent Multipath Routing and the Butterfly Network}

%\author{Edward L. Platt}
%\affiliation{%
%  \institution{University of Michigan\\School of Information}
%  \city{Ann Arbor} 
%  \state{Michigan} 
%}
%\email{elplatt@umich.edu}

%\author{Daniel M. Romero}
%\affiliation{%
%  \institution{University of Michigan\\School of Information}
%  \city{Ann Arbor} 
%  \state{Michigan} 
%}
%\email{drom@umich.edu}
\author{Anonymized\\for\\blind review}

% The default list of authors is too long for headers.
%\renewcommand{\shortauthors}{E.L. Platt and D.M. Romero.}
\renewcommand{\shortauthors}{Anonymized for blind review}

\begin{abstract}
It is crucial for large-scale communication networks such as the internet
to be resilient against attacks\cite{sterbenz_resilience_2010}
such as censorship and surveillance,
which pose a threat to free expression and free association.
Self-organized networks such as the internet’s router network typically have
heavy-tailed degree distributions\cite{barabasi_scale-free_2009},
making them highly vulnerable to targeted attacks against central nodes
\cite{albert_error_2000}.
While cryptographic solutions exist,
they fail to address the underlying topological problem,
and remain vulnerable to
man-in-the-middle attacks \cite{nayak_different_2010}
and coercion \cite{grewal_caveat_2013}.
Coercion-resistant, topological approaches to attack tolerance are needed to
address the current vulnerability of communications infrastructure to
censorship and surveillance.
We present a novel concurrent multipath routing (CMR) algorithm for the
wraparound butterfly network topology,
as well as a highly attack-tolerant Structured Multipath Fault Tolerance (SMFT)
architecture which incorporates the butterfly CMR algorithm. We also identify a
previously unexplored relationship between network topology, trust transitivity,
and attack-tolerance, and provide a framework for further exploration of this
relationship. Our work is the first theoretical demonstration of a point-to-point
communication network architecture that can resist coercion and other
non-technical attacks, without requiring infinitely transitive trust.
To address cases where the network structure cannot be fully controlled,
we demonstrate how a snapshot of the internet’s router network can be partially
rewired for greater attack-tolerance.
More broadly, we hope that this work will serve as a starting point for the
development of additional topology-based attack-tolerant communication
architectures to guard against the dangers of censorship and surveillance.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002978.10002986</concept_id>
<concept_desc>Security and privacy~Formal methods and theory of security</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003033.10003034</concept_id>
<concept_desc>Networks~Network architectures</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10010940.10010971.10010972.10010540</concept_id>
<concept_desc>Software and its engineering~Peer-to-peer architectures</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Security and privacy~Formal methods and theory of security}
\ccsdesc[500]{Networks~Network architectures}
\ccsdesc[500]{Software and its engineering~Peer-to-peer architectures}

\keywords{
Adversarial Faults,
Resilience,
Butterfly Network,
Fault Tolerance,
Multipath Routing,
Censorship,
Decentralization}

\maketitle

\section{Introduction}

@@

Coercion-resistant, topological approaches to attack tolerance are needed to
address the current vulnerability of communications infrastructure
to censorship and surveillance.
This paper presents several contributions towards advancing those goals.
While our work is motivated by the network of internet routers,
the results are theoretical,
and can potentially be applied to many different types of networks,
whether made of physical wires, virtual tunnels,
or other types of links.

@@

\section{Background and Related Work}
\label{sec-related}

@@

All existing attack-tolerant networks we are aware of are content-addressable
networks (CANs) in which data is stored and retrieved based on key values,
rather than point-to-point networks, in which data is communicated between
two parties.
Fiat and Saia described a scheme that combines the butterfly topology
with expander graphs to create a highly censorship-resistant,
content-addressable network \cite{fiat_censorship_2002},
although this scheme does not scale well and is impractical due to a
high level of data replication.
Perhaps the most mature structural solution is the Freenet collaboration
\cite{clarke_freenet:_2001}.
Freenet uses secret sharing
\cite{shamir_how_1979, blakley_safeguarding_1979}
and small-world routing
\cite{zhang_using_2002,kleinberg_small-world_2000}
to create a content-addressable network with a high level of both
confidentiality and censorship resistance.
Freenet guarantees that data is stored redundantly,
but still allows for centralized network structure,
and thus single points of failure,
as data travels from its origin to the redundant storage locations.
Unlike the above content-addressable networks, our architecture is purely network based
and does not require nodes to store data indefinitely.
Our architecture also improves on the scalablity of the Fiat-Saia network,
and makes requirements about network topology explicit.

{\em Multipath routing} protocols identify multiple paths between
source and destination
in contrast to traditional {\em unipath} routing, which uses
a single path.
The special case of {\em concurrent} multipath routing uses mutliple paths
simultaneously.
Multipath routing has many applications, including reduced congestion,
increased throughput, and more reliability
\cite{qadir_exploiting_2015}.
Many of these routing protocols offer increased confidentiality
\cite{zin_survey_2015}.
Some approaches utilize redundant paths as backups for increased
fault tolerance
\cite{alrajeh_secure_2013},
and some specifically protect against adversarial faults
\cite{kohno_improvement_2012, khalil_unmask:_2010, lou_h-spread:_2006}.
Most work on multipath routing has been motivated by applications related to
wireless sensor networks (WSNs),
and have thus focused on ad hoc, unstructured networks, often having a central
base station.
The method of Liu et al.
\cite{liu_secure_2012}
routes multiple messages first to random peers and then
to a central base station,
with the network edges constrained by sensors' physical location.
We have found very few examples of CMR applied to {\em adversarial}
fault tolerance in the existing literature,
and all have focused on ad-hoc wireless sensor networks, without attention
to the role of network structure.
The alogorithm we present for the butterfly topology complements existing work
by addressing cases where links are not constrained by physical
distance,
and where network structure can be engineered for greater attack-tolerance.

@@

Our proposed architecture is differentiated from existing systems by several
properties (Table \ref{tab:compare}).
Decentralized architectures are more resistent to coercion
\cite{grewal_caveat_2013}
and man-in-the-middle attacks \cite{nayak_different_2010}.
Trust-based systems are more sustainable than proof-of-work.
Bounded-trust systems do not require the unrealistic assumption of infinite
trust transitivity.
Topological approaches address the root cause of vulnerability
in heavy-tail networks,
rather than relying on technology that can be side-stepped through coercion.
Point-to-point communication allows two individuals to exchange messages
without requiring large amounts of indefinite data storage on intermediate
nodes.

\begin{table*}[t!]
\caption{Comparison of attack-tolerant network communication architectures.\label{tab:compare}}
\begin{center}
\begin{tabular}{l|ccccc}
                              & Decentralized & Trust-based & Bounded-trust & Topological & Point-to-point \\
\hline
Public Key Infrastructure     &               & \cmark      & \cmark        &             & \cmark     \\
Web of Trust                  & \cmark        & \cmark      &               &             & \cmark     \\
Freenet                       & \cmark        & \cmark      & \cmark        &             &            \\
Federated Byzantine Agreement & \cmark        & \cmark      & \cmark        &             & \cmark     \\
Proof of Work/Blockchain      & \cmark        &             & \cmark        &             &            \\
Fiat-Saia                     & \cmark        & \cmark      & \cmark        & \cmark      &            \\
Structured Multipath FT       & \cmark        & \cmark      & \cmark        & \cmark      & \cmark     \\
\hline
\end{tabular}
\end{center}
\end{table*}

\section{Trust Networks and Fault Tolerance}
\label{sec-ft}

@@

\subsection{Multipath Fault Tolerance}

Standard fault tolerance methods use redundancy to detect and correct
statistically independent faults.
In complex networks however, faults can be correlated when,
for example, two messages pass through the same faulty node.
For now, let us assume our sender (Alice) and receiver (Bob) are connected
by $\delta$ direct channels, with indpendent errors.
We will return to the question of constructing these channels in subsequent
sections.
For now, we concern ourselves with the question:
given that the network provides $\delta$ redundant channels between
Alice and Bob,
what is the probability that an adversary (Mal) causes an undetectable
error after causing faults in a fixed number of channels?

Let us first consider the scenario in which
Alice sends a message copy over each available channel.
We can also assume that each message includes the number of messages sent,
the full list of channels used, etc.,
making that information available to Bob.
When Bob receives the messages, there are several possibilities.
If some of the messages are missing
or if some of the messages disagree,
Bob knows that some of the messages were either blocked or altered,
and he has successfully tolerated the fault(s).
Bob can then take any of several actions:
1. request retransmission;
2. send receipts so Alice knows which paths have been compromised;
or 3. attempt error correction using majority voting.
If instead, Bob finds that all the messages are present and agree,
there are two possible cases.
The first case is that Mal has not compromised any of the messages,
and Bob has correctly accepted them, so no failure has occurred.
The second case is that Mal has compromised {\em all} of the messages,
so Bob has accepted an erroneous message and a failure has occurred.
In the present scenario,
whether a failure occurs depends only on whether Mal has the resources to
compromise all of the channels.
In a more realistic scenario,
both Alice and Mal have limited resources and are not able to use or
compromise all available channels.

@@

Figure \ref{fig:pfail} shows the value of $p_f$
as a function of $k$ and $l$.
Equation (\ref{eq:pf_approx}) shows that while $p_f$
depends on the fractions of
channels actually utilized $\alpha$ and compromised $\beta$,
it decreases exponentially with $\delta$.
This result is significant because,
as we will soon show, $\delta$
depends only on the network structure
and the strength of trust transitivity.
{\em Thus, the scheme can be effective, even when the number of channels used
$k$ is a small fraction of the channels available}.
In other words, this scheme exhibits a {\em stabilizing asymmetry:}
senders can tolerate attacks from significantly more powerful
adversaries,
as long as the network provides large $\delta$.

\begin{figure}
\centerline{\includegraphics{fig-perror}}
\caption{
The probability of an undetectable error as a function of the number of
redundant channels and the number of adversarial faults.
}
\label{fig:pfail}
\end{figure}

\subsection{Bounded Trust Model}

So far, we have assumed that Alice and Bob have access to some number
$\delta$ of channels with statistically indpendent faults.
However, in real communication architectures, direct links between all
pairs of individuals are not possible and messages must be routed through
a number of intermediate nodes.
In an adversarial setting,
the existence of intermediate nodes introduces two problems:
1. intermediate nodes may be compromised by the adversary and
2. faults on paths are no longer statistically independent:
two paths may pass through the same compromised node.
We show how to how to resolve these problems using a combination of network
structure and bounded trust transitivity.

@@

An alternative assumption might be that each hop away from Alice in
in the network reduces the probability that a node can resist compromise
by a multiplicatve constant.
Such a situation could occur if nodes more distant from Alice are
more favorably disposed to Alice's adversary, more likely to cooperate with that
adversary, or less likely to take proactive security measures against that
adversary.
An even simpler version assumes that nodes up to some
fixed number of hops cannot be compromised, and that those beyond can.
This simplified version is still more realistic than infinite transitivity
and will be convenient for proving our results.
We now proceed to define our model formally.

We define the {\em bounded trust model} on
an undirected graph $G = (V,E)$,
although the model can easily be extended to directed multigraphs.
Vertices representing commiunicating parties,
with edges representing mutually trusted communication links.
We define a {\em trust radius} $h$ such that nodes $v$ and
$w$ trust each other if their distance is less than $h$.
For a given node $v$,
we call the set of trusted nodes its
{\em trusted neighborhood} $T_h(v)$,
and all nodes at exactly distance $h$ the
{\em trust boundary} $B_h(v)$:
\beq
T_h(v) &=& \left\{ w \mid d(v,w) < h \right\} \\
B_h(v) &=& \left\{ w \mid d(v,w) = h \right\}.
\eeq
The trust boundary $B_h$ plays an important role because these nodes are not
trusted by $u$,
and if compromised can entirely isolate $v$ from the rest of the network.

Now let $s \in V$ be an arbitrary sender
and $t \in V$ be an arbitrary receiver.
We assume the presence of an adversary who knows the
full structure of the network,
and who can compromise a fixed number of nodes,
gaining complete control of their behavior.
We also assume that the adversary is specifically targeting communicaiton
between $s$ and $t$ and
can compromise any node except for those trusted by $s$ or $t$.
Under these trust assumptions, adversarial faults can only occur
outside the trusted neighborhoods of $s$ and $t$:
$V \setminus \left(T_h(v) \cup T_h(w)\right)$.
We refer to this set of nodes as the {\em untrusted region}.
We now show how it is possible to communicate reliably,
even when all available paths go through the untrusted region.

\subsection{Effective Redundancy}

Our approach is to achieve fault tolerance through redundancy.
To do so, we must use only
{\em independent paths} \cite{reiter_resilient_1998},
which have no common points of failure.
Typically, it is assumed that in order to be independent,
paths must be internally vertex disjoint, i.e.,
have no nodes in common except the endpoints.
However, under the bounded trust model,
intersecting paths can still be independent if their
intersection contains only trusted nodes.
We define two paths with common endpoints
to be {\em $h$-internally vertex disjoint}
if all common vertices are less than distance $h$ from
one of the endpoints.
This condition holds if and only if two paths are indpendent
under the bounded trust model with radius $h$.

>>>>

% Template for PLoS
% Version 3.5 March 2018
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file 
% and leave only the final text of your manuscript. 
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8x]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
\usepackage{setspace} 
\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

\usepackage{booktabs} % For formal tables
\usepackage{epigraph}
\usepackage{afterpage}
\usepackage{tikz}
\usepackage{soul}
\usepackage[framemethod=tikz]{mdframed}
\usetikzlibrary{arrows,chains,decorations.pathreplacing}
\usepackage{pifont} % http://ctan.org/pkg/pifont
\usepackage{amsthm}

%% Include all macros below

\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}
\newcommand{\bhlpar}{\begin{mdframed}[innerleftmargin=0,innerrightmargin=0,hidealllines=true,backgroundcolor=yellow!20]}
\newcommand{\ehlpar}{\end{mdframed}}
\DeclareMathOperator{\wbf}{wBF}
\newtheorem{theorem}{Theorem}
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Towards attack tolerant networks: concurrent multipath routing and the butterfly network} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Edward L. Platt\textsuperscript{1,*},
Daniel M. Romero\textsuperscript{1}
\\
\bigskip
\textbf{1} School of Information, University of Michigan, Ann Arbor, Michigan, USA
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.

% Current address notes
%\textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
% \textcurrency b Insert second current address 
% \textcurrency c Insert third current address

% Deceased author note
%\dag Deceased

% Group/Consortium Author Note
%\textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* elplatt@umich.edu

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
It is crucial for large-scale communication networks such as the internet
to be resilient against attacks\cite{sterbenz_resilience_2010}
such as censorship and surveillance,
which pose a threat to free expression and free association.
Self-organized networks such as the internet’s router network typically have
heavy-tailed degree distributions\cite{barabasi_scale-free_2009},
making them highly vulnerable to targeted attacks against central nodes
\cite{albert_error_2000}.
While cryptographic solutions exist,
they fail to address the underlying topological problem,
and remain vulnerable to
man-in-the-middle attacks \cite{nayak_different_2010}
and coercion \cite{grewal_caveat_2013}.
Coercion-resistant, topological approaches to attack tolerance are needed to
address the current vulnerability of communications infrastructure to
censorship and surveillance.
We present a novel concurrent multipath routing (CMR) algorithm for the
wraparound butterfly network topology,
as well as a highly attack-tolerant Structured Multipath Fault Tolerance (SMFT)
architecture which incorporates the butterfly CMR algorithm. We also identify a
previously unexplored relationship between network topology, trust transitivity,
and attack-tolerance, and provide a framework for further exploration of this
relationship. Our work is the first theoretical demonstration of a point-to-point
communication network architecture that can resist coercion and other
non-technical attacks, without requiring infinitely transitive trust.
To address cases where the network structure cannot be fully controlled,
we demonstrate how a snapshot of the internet’s router network can be partially
rewired for greater attack-tolerance.
More broadly, we hope that this work will serve as a starting point for the
evelopment of additional topology-based attack-tolerant communication
architectures to guard against the dangers of censorship and surveillance.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
%\section*{Author summary}
%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

\linenumbers

% Use "Eq" instead of "Equation" for equation citations.
\section*{Introduction}

@@

Coercion-resistant, topological approaches to attack tolerance are needed to
address the current vulnerability of communications infrastructure
to censorship and surveillance.
This paper presents several contributions towards advancing those goals.
While our work is motivated by the network of internet routers,
the results are topological,
and can potentially be applied to many different types of networks.

@@

\section*{Background and Related Work}
\label{sec-related}

@@

All existing attack-tolerant networks we are aware of are content-addressable
networks (CANs) in which data is stored and retrieved based on key values,
rather than point-to-point networks, in which data is communicated between
two parties.
Fiat and Saia described a scheme that combines the butterfly topology
with expander graphs to create a highly censorship-resistant,
content-addressable network \cite{fiat_censorship_2002},
although this scheme requires high levels of data replication and indefinite
storage.
Perhaps the most mature structural solution is the Freenet collaboration
\cite{clarke_freenet:_2001}.
Freenet uses secret sharing
\cite{shamir_how_1979, blakley_safeguarding_1979}
and small-world routing
\cite{zhang_using_2002,kleinberg_small-world_2000}
to create a content-addressable network with a high level of both
confidentiality and censorship resistance.
Freenet guarantees that data is stored redundantly,
but still allows for centralized network structure,
and thus single points of failure,
as data travels from its origin to the redundant storage locations.
Unlike the above content-addressable networks, our architecture is purely network based
and does not require nodes to store data indefinitely.
Our architecture also improves on the scalablity of the Fiat-Saia network,
and makes requirements about network topology explicit.

{\em Multipath routing} protocols identify multiple paths between
source and destination
in contrast to traditional {\em unipath} routing, which uses
a single path.
The special case of {\em concurrent} multipath routing uses multiple paths
simultaneously.
Multipath routing has many applications, including reduced congestion,
increased throughput, and more reliability
\cite{qadir_exploiting_2015}.
Many of these routing protocols offer increased confidentiality
\cite{zin_survey_2015}.
Some approaches utilize redundant paths as backups for increased
fault tolerance
\cite{alrajeh_secure_2013},
and some specifically protect against adversarial faults
\cite{kohno_improvement_2012, khalil_unmask:_2010, lou_h-spread:_2006}.
Most work on multipath routing has been motivated by applications related to
wireless sensor networks (WSNs),
and have thus focused on ad-hoc, unstructured networks, often having a central
base station.
The method of Liu et al.
\cite{liu_secure_2012}
routes multiple messages first to random peers and then
to a central base station,
with the network edges constrained by sensors' physical location.
We have found very few examples of CMR applied to {\em adversarial}
fault tolerance in the existing literature,
and all have focused on ad-hoc wireless sensor networks, without attention
to the role of network structure.

@@

Our proposed architecture is differentiated from existing systems by several
properties (Table \ref{tab:compare}).
Decentralized architectures are more resistant to coercion
\cite{grewal_caveat_2013}
and man-in-the-middle attacks \cite{nayak_different_2010}.
Trust-based systems are more sustainable than proof-of-work.
Bounded-trust systems do not require the unrealistic assumption of infinite
trust transitivity.
Topological approaches address the root cause of vulnerability
in heavy-tail networks,
rather than relying on technology that can be side-stepped through coercion.
Point-to-point communication allows two individuals to exchange messages
without requiring large amounts of indefinite data storage on intermediate
nodes.

\begin{table*}[t!]
\caption{Comparison of attack-tolerant network communication architectures.\label{tab:compare}}
\begin{center}
\begin{tabular}{l|p{0.6in}p{0.6in}p{0.6in}p{0.6in}p{0.6in}}
                              & Decentra-lized & Trust-based & Bounded-trust & Topo-logical & Point-to-point \\
\hline
PKI            &               & \cmark      & \cmark        &             & \cmark     \\
Web of Trust   & \cmark        & \cmark      &               &             & \cmark     \\
Freenet        & \cmark        & \cmark      & \cmark        &             &            \\
FBA            & \cmark        & \cmark      & \cmark        &             & \cmark     \\
Proof of Work  & \cmark        &             & \cmark        &             &            \\
Fiat-Saia      & \cmark        & \cmark      & \cmark        & \cmark      &            \\
SMFT           & \cmark        & \cmark      & \cmark        & \cmark      & \cmark     \\
\hline
\end{tabular}
\end{center}
\end{table*}

\section*{Trust Networks and Fault Tolerance}
\label{sec-ft}

@@

\subsection*{Multipath Fault Tolerance}

Standard fault tolerance methods use redundancy to detect and correct
statistically independent faults.
In complex networks however, faults can be correlated when,
for example, two messages pass through the same faulty node.
For now, let us assume our sender (Alice) and receiver (Bob) are connected
by $\delta$ direct channels, with independent errors.
We will return to the question of constructing these channels in subsequent
sections.
For now, we concern ourselves with the question:
given that the network provides $\delta$ redundant channels between
Alice and Bob,
what is the probability that an adversary (Mal) causes an undetectable
error after causing faults in a fixed number of channels?

Let us first consider the scenario in which
Alice sends a message copy over each available channel.
We can also assume that each message includes the number of messages sent,
the full list of channels used, etc.,
making that information available to Bob.
When Bob receives the messages, there are several possibilities.
If some of the messages are missing
or if some of the messages disagree,
Bob knows that some of the messages were either blocked or altered,
and he has successfully tolerated the fault(s).
Bob can then take any of several actions:
1. request re-transmission;
2. send receipts so Alice knows which paths have been compromised;
or 3. attempt error correction using majority voting.
If instead, Bob finds that all the messages are present and agree,
there are two possible cases.
The first case is that Mal has not compromised any of the messages,
and Bob has correctly accepted them, so no failure has occurred.
The second case is that Mal has compromised {\em all} of the messages,
so Bob has accepted an erroneous message and a failure has occurred.
In the present scenario,
whether a failure occurs depends only on whether Mal has the resources to
compromise all of the channels.
In a more realistic scenario,
both Alice and Mal have limited resources and are not able to use or
compromise all available channels.

@@

Fig. \ref{fig:pfail} shows the value of $p_f$
as a function of $k$ and $l$.
Eq. (\ref{eq:pf_approx}) shows that while $p_f$
depends on the fractions of
channels actually utilized $\alpha$ and compromised $\beta$,
it decreases exponentially with $\delta$.
This result is significant because,
as we will soon show, $\delta$
depends only on the network structure
and the strength of trust transitivity.
{\em Thus, the scheme can be effective, even when the number of channels used
$k$ is a small fraction of the channels available}.
In other words, this scheme exhibits a {\em stabilizing asymmetry:}
senders can tolerate attacks from significantly more powerful
adversaries,
as long as the network provides large $\delta$.

\begin{figure}[!h]
\centerline{\includegraphics{fig-perror}}
\caption{
The probability of an undetectable error as a function of the number of
redundant channels and the number of adversarial faults.
}
\label{fig:pfail}
\end{figure}

\subsection*{Bounded Trust Model}

So far, we have assumed that Alice and Bob have access to some number
$\delta$ of channels with statistically independent faults.
However, in real communication architectures, direct links between all
pairs of individuals are not possible and messages must be routed through
a number of intermediate nodes.
In an adversarial setting,
the existence of intermediate nodes introduces two problems:
1. intermediate nodes may be compromised by the adversary and
2. faults on paths are no longer statistically independent:
two paths may pass through the same compromised node.
We show how to how to resolve these problems using a combination of network
structure and bounded trust transitivity.

@@

An alternative assumption might be that each hop away from Alice in
in the network reduces the probability that a node can resist compromise
by a multiplicative constant.
Such a situation could occur if nodes more distant from Alice are
more favorably disposed to Alice's adversary, more likely to cooperate with that
adversary, or less likely to take proactive security measures against that
adversary.
An even simpler version assumes that nodes up to some
fixed number of hops cannot be compromised, and that those beyond can.
This simplified version is still more realistic than infinite transitivity
and will be convenient for proving our results.
We now proceed to define our model formally.

We define the {\em bounded trust model} on
an undirected graph $G = (V,E)$,
although the model can easily be extended to directed multigraphs.
Vertices representing communicating parties,
with edges representing mutually trusted communication links.
We define a {\em trust radius} $h$ such that nodes $v$ and
$w$ trust each other if their distance is less than $h$.
For a given node $v$,
we call the set of trusted nodes its
{\em trusted neighborhood} $T_h(v)$,
and all nodes at exactly distance $h$ the
{\em trust boundary} $B_h(v)$:
\beq
T_h(v) &=& \left\{ w \mid d(v,w) < h \right\} \\
B_h(v) &=& \left\{ w \mid d(v,w) = h \right\}.
\eeq
The trust boundary $B_h$ plays an important role because these nodes are not
trusted by $u$,
and if compromised can entirely isolate $v$ from the rest of the network.

Now let $s \in V$ be an arbitrary sender
and $t \in V$ be an arbitrary receiver.
We assume the presence of an adversary who knows the
full structure of the network,
and who can compromise a fixed number of nodes,
gaining complete control of their behavior.
We also assume that the adversary is specifically targeting communication
between $s$ and $t$ and
can compromise any node except for those trusted by $s$ or $t$.
Under these trust assumptions, adversarial faults can only occur
outside the trusted neighborhoods of $s$ and $t$:
$V \setminus \left(T_h(v) \cup T_h(w)\right)$.
We refer to this set of nodes as the {\em untrusted region}.
We now show how it is possible to communicate reliably,
even when all available paths go through the untrusted region.

\subsection*{Effective Redundancy}

Our approach is to achieve fault tolerance through redundancy.
To do so, we must use only
{\em independent paths} \cite{reiter_resilient_1998},
which have no common points of failure.
Typically, it is assumed that in order to be independent,
paths must be internally vertex disjoint, i.e.,
have no nodes in common except the endpoints.
However, under the bounded trust model,
intersecting paths can still be independent if their
intersection contains only trusted nodes.
We define two paths with common endpoints
to be {\em $h$-internally vertex disjoint}
if all common vertices are less than distance $h$ from
one of the endpoints.
This condition holds if and only if two paths are independent
under the bounded trust model with radius $h$.
